%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{EXPERIENCE}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries2}
  \cventrynew{\textbf{Franklin Templeton Investments}, \textnormal{\textbf{Lead Data Engineer} | Hyderabad, India}}{Aug 2020 -- Present}{
\vspace{2mm}\begin{cvitems}
\frenchspacing
          \item Orchestrated deployment of a Copilot Studio–powered chatbot for Compliance, earning runner-up in a global PoC showcase.
          \item Engineered a Streamlit application to classify and enrich third-party distribution data via Databricks Llama endpoints and Crew.ai, accelerating data quality efforts.
          \item Migrated Azure Databricks workloads (ADLS Gen2) to AWS with UC workflow upgrades during a major cloud consolidation—streamlined operations across teams.
          \item Implemented a production-grade, fine-tuned SparkNLP NER solution, standardizing entity extraction at minimal cost.
          \item Spearheaded Xceptor-based automation of 105+ internal processes, realizing 260 man-days in annual savings and significantly reducing error rates.
      \end{cvitems}
  }
  \cventrynew{\textbf{SpringML Inc.}, \textnormal{\textbf{Senior Data Engineer} | Hyderabad, India}}{Nov 2018 -- Aug 2020}{
      \vspace{2mm}\begin{cvitems}
\frenchspacing
          \item Architected and optimized end-to-end ML pipelines on GCP (Kubeflow, TFX, Composer), enabling seamless model training \& serving.
          \item Developed ETL jobs to ingest and transform terabyte-scale data into BigQuery, Bigtable, and Cloud Storage—accelerating analytics readiness.
          \item Designed and deployed Angular/React UIs and Python Flask back-ends on App Engine for real-time dashboards and data APIs.
          \item Migrated legacy Hadoop workloads to GCP Dataproc, streamlining Spark job orchestration and reducing infrastructure costs.
          \item \textbf{Key Clients:}
          \begin{itemize}
              \item \textbf{Publishers Clearing House} – Automated ML model lifecycle (Kubeflow, KFServing) with CI/CD, yielding \$142K annual savings.
              \item \textbf{CBRE Inc.} – Engineered secure GCP VPCs, VPNs, Dataflow pipelines, and BigQuery schemas for enterprise data migration.
              \item \textbf{iHuddl Investments} – Built real-time dashboards (Angular, D3.js), WebSocket data pipelines, and scalable App Engine services.
          \end{itemize}
      \end{cvitems}
  }
  \cventrynew{\textbf{ScriptBees IT Pvt Ltd.}, \textnormal{\textbf{Senior Software Engineer} | Hyderabad, India}}{Feb 2017 -- Oct 2018}{
      \vspace{2mm}\begin{cvitems}
\frenchspacing
          \item Designed PySpark architectures and authored fuzzy-logic engines for invoice processing (EY GST solution).
          \item Scraped and structured multi-source news data using BeautifulSoup and Dryscrape for a regional media portal (PTI/INS).
          \item Developed RPA bots (Automagica, Python) and integrated testing pipelines via Jenkins for Verizon Wireless process automation.
      \end{cvitems}
  }
\cventrynew{Tech Mahindra Limited, \textnormal{\textbf{Software Engineer} | Hyderabad, India}}{Sept 2014 -- Jan 2017}{
    \vspace{2mm}\begin{cvitems}
\frenchspacing
      \item Processed and provisioned OSS/BSS orders for TalkTalk \& BT integration, enhancing order-tracking portals.
      \item Led data exploration, feature engineering (SciPy, Pandas), and visualization (Matplotlib) for retail analytics on the X-Retail platform.
    \end{cvitems}
  }
\end{cventries2}
